---
title: Wealth and Skill
author: TimelyPortfolio
license: by-nc-sa
widgets: [bootstrap]
github: {user: timelyportfolio, repo: talks/2014-04-15_UofA}
mode: selfcontained
hitheme: solarized_light
assets:
  css:
  - "http://fonts.googleapis.com/css?family=Raleway:300"
  - "http://fonts.googleapis.com/css?family=Oxygen"
--- dt:10
  
<style>
iframe.rChart{
  height:450px;
  width:100%;
  margin:auto auto;
}

body{
  font-family: 'Oxygen', sans-serif;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

h3 {
  background-color: #D4DAEC;
  font-size:110%;
    text-indent: 100px; 
}

h4 {
  text-indent: 100px;
}

address {
  font-size: 9px;
  line-height: 14px;
/*  position: absolute;
  right:100px;
  width:300px;*/
}

blockquote {
  background-color:rgb(38, 41, 35)
}

.title-slide {
  background-color: rgba(173, 177, 152, 0.31);
}
</style>

```{r message = F, warning = F, error = F, echo = F, tidy = F, cache = F}
require(knitr)
opts_chunk$set(
  message = F,
  warning = F,
  echo = F,
  error = F,
  tidy = F,
  cache = F,
  fig.width = 11,
  fig.height = 5,
  results = 'asis'
)
```

## Why Am I Here?

---

## Why Are You Here?

--- 

### Forbes 400 (2013) | How They Made Their Money?

```{r}
require(rCharts);require(rjson)

#modify show without reinstall to fix the height
Dimple2 <- setRefClass(
  "Dimple2",
  contains = "Dimple",
  methods = list(
    initialize = function(){
      callSuper(); 
    },
    #override the show here
    show = function (mode_ = NULL, ...) 
    {
        mode_ = getMode(mode_)
        switch(mode_, static = {
            viewer = getOption("viewer")
            if (!grepl("^http", LIB$url) && !is.null(viewer)) {
                temp_dir = tempfile(pattern = "rCharts")
                dir.create(temp_dir)
                suppressMessages(copy_dir_(LIB$url, file.path(temp_dir, 
                    LIB$name)))
                tf <- file.path(temp_dir, "index.html")
                writeLines(.self$render(..., static = F), tf)
                viewer(tf)
            } else {
                writeLines(.self$render(..., static = T), tf <- tempfile(fileext = ".html"))
                if (!is.null(viewer)) {
                    viewer(tf)
                } else {
                    browseURL(tf)
                }
            }
        }, server = {
            shiny_copy = .self$copy()
            shiny_copy$params$dom = "show"
            assign(".rChart_object", shiny_copy, envir = .GlobalEnv)
            if (packageVersion("shiny") > 0.7) {
                brwsr <- getOption("viewer", interactive())
            } else {
                brwsr <- getOption("shiny.launch.browser", interactive())
            }
            shiny::runApp(file.path(system.file(package = "rCharts"), 
                "shiny"), launch.browser = brwsr)
        }, inline = {
            add_ext_widgets(lib)
            return(.self$print(...))
        }, iframe = {
            chunk_opts_ = opts_current$get()
            file_ = knitr:::fig_path(".html", chunk_opts_)
            if (!file.exists(dirname(file_))) {
                dir.create(dirname(file_))
            }
            cdn = !(chunk_opts_$rcharts %?=% "draft")
            .self$save(file_, cdn = cdn)
            writeLines(
              sprintf(
                "<iframe src='%s'
                scrolling='no' seamless class='rChart %s' id=iframe-%s
                height=%s width = %s
                ></iframe>"
                ,file_
                ,lib
                ,params$dom
                ,params$height
                ,params$width
              )
            )
            return(invisible())
        }, iframesrc = {
            writeLines(
              c(
                "<iframe srcdoc='", htmlspecialchars(.self$render(...)), 
                "' scrolling='no' seamless class='rChart ",
                lib, 
                " ' height = ",
                paste0(params$height,"px"),
                " ' width = ",
                paste0(params$width,"px"),                
                paste0("id='iframe-", params$dom, "'>"),
                "</iframe>"
              )
            )
            return(invisible())
        })
    }
))

dPlot2 <- function(x, data, ...){
  myChart <- Dimple2$new()
  myChart$getChartParams(x, data, ...)
  #set these to dimple since use all of its config.yml and layouts
  #dimple2 will not exist
  myChart$setLib("dimple")
  #make this blank by default
  #not sure why this does not happen when overriding refclass
  myChart$setTemplate(afterScript="<script></script>")
  return(myChart$copy())
}

wealthData <- data.frame(
  industry = c(
    "Investments","Technology","Real Estate","Fashion and Retail","Media","Food and Beverage","Energy","Healthcare","Sports","Manufacturing"
    ,"Investments","Service","Fashion and Retail","Energy","Food and Beverage","Media","Manufacturing","Real Estate","Diversified","Technology","Healthcare"
  )
  ,selfmade = c(rep(T,10),rep(F,11))
  ,freq = c(
    c(77,45,22,18,17,15,12,11,10,10)/273
    ,c(19,17,17,16,14,11,10,5,3,3,3)/(400-273)
  )
)

n1 <- nPlot(
  freq ~ industry
  ,group = "selfmade"
  ,data = wealthData
  ,type = "multiBarHorizontalChart"
)
n1$yAxis(
  tickFormat = "#! function(d) { return d3.format('0.2%')(d) }!#"
)
#n1

d1 <- dPlot2(
  y = c("industry","selfmade")
  ,x = "freq"
  ,groups = "industry"
  ,data = wealthData
  ,type = "line"
  ,defaultColors = "#!d3.scale.category20()!#"
  ,height = 450
  ,width = 900
  ,bounds = list( x = 250, y = 20, width = 650, height = 400)
)
d1$xAxis(
  type = "addMeasureAxis"
  ,outputFormat = "0.2%"
)
d1$yAxis(
  type = "addCategoryAxis"
  ,orderRule = "freq"
)
d1
```
<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href = "http://www.forbes.com/sites/erincarlyle/2013/09/18/how-self-made-forbes-400-billionaires-earned-their-money/">
      How Self-Made Forbes 400 Billionaires Earned Their Money
    </a><br>
    Erin Carlyle<br>
    Forbes September 18, 2013
</address>
</div>
</div>


--- dt:10

### Forbes 400 (2013) | How They Made Their Money? | Bar Chart


```{r}
d2 <- dPlot2(
  y = c("industry","selfmade")
  ,x = "freq"
  ,groups = "selfmade"
  ,data = wealthData
  ,type = "bar"
  ,defaultColors = "#!d3.scale.category20()!#"
  ,height = 450
  ,width = 900
  ,bounds = list( x = 250, y = 20, width = 650, height = 400)
)
d2$xAxis(
  type = "addMeasureAxis"
  ,outputFormat = "0.2%"
)
d2$yAxis(
  type = "addCategoryAxis"
  ,orderRule = "freq"
)
d2
```
<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href = "http://www.forbes.com/sites/erincarlyle/2013/09/18/how-self-made-forbes-400-billionaires-earned-their-money/">
      How Self-Made Forbes 400 Billionaires Earned Their Money
    </a><br>
    Erin Carlyle<br>
    Forbes September 18, 2013
</address>
</div>
</div>

---

### More About Becoming Ultra-Wealthy

<div class="row">
<div class = "col-md-8">
```{r}
d3 <- dPlot2(
  Source ~ Percentage
  ,groups = "Source"
  ,data=data.frame(
    Source = c("Business Ownership", "Wealth Management", "Marriage and Inheritance","Real Estate")
    ,Percentage = c(.60,.20,.12,.08)
  )  
  ,type = "bar"
  ,defaultColors = "#!d3.scale.category20()!#"
  ,height = 450
  ,width = 620
  ,bounds = list( x = 150, y = 20, width = 500, height = 400)
)
d3$xAxis(
  type = "addMeasureAxis"
  ,outputFormat = "0.2%"
)
d3$yAxis(
  type = "addCategoryAxis"
  ,orderRule = "Percentage"
)
#d3$setTemplate(
#  chartDiv = "<{{container}} id = {{chartId}} height = {{height}} width = 100%></{{ #container}}>"
#)
d3
```
  </div>
  <div class="col-md-4">
    <br><br>
    <blockquote style="font-size:80%;line-height:20px;">
    "Wealth mobility, it turns out, requires idiosyncratic risk, concentration, and (nonrecourse) leverage--all factors that MPT seeks to eliminate in a standard diversified portfolio."
    </blockquote>
  </div>
</div>
<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href = "A Risk-Based Asset Allocation Framework for Unstable Markets">
      A Risk-Based Asset Allocation Framework for Unstable Markets
    </a><br>
    Ashvin B. Chhabra<br>
    CFA Article Collections for Practitioners<br>
    October 2013, Vol. 29, No. 4<br>
    (doi: 10.2469/cp.v29.n4.1)
</address>
</div>
</div>

---

### Luck and Skill in Wealth | Wealth Concentration

<div class="row">
  <div class = "col-md-8">
    <img src = "./assets/fig/fernholz_wealth.png" height = 500px></img>
  </div>
  <div class="col-md-4">
    <br><br>
    <blockquote style="font-size:80%;line-height:20px;">
    "In the absence of any redistribution, the distribution of wealth is unstable over time and becomes concentrated entirely at the top. This occurs despite the fact that all households have identical patience and skill."
    </blockquote>
  </div>  
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href ="http://www.ricardofernholz.com/Instability.pdf">
      Instability and Concentration in the Distribution of Wealth (Draft)
    </a><br>
    Fernholz, R and R Fernholz<br>
    Claremont Mckenna College / Intech<br>
    December 9, 2103<br>
</address>
</div>
</div>


---

### Luck and Skill in Wealth | Skill Continuum

<div class="row">
  <div class = "col-md-8">
    <br>
    <img src = "./assets/fig/mauboussin_continuum.png" height = 250px></img>
  </div>
  <div class="col-md-4">
    <br><br>
    <blockquote style="font-size:80%;line-height:20px;">
    "There are three aspects I will emphasize. The first is related to the number of players...second aspect is sample size...Finally, there's the aspect of how the game is scored."
    </blockquote>
  </div>  
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href ="http://analystreports.som.yale.edu/internal/F2013/MJ/Alpha%20and%20the%20Paradox%20of%20Skill.pdf">
      Luck and Skill Untangled: The Science of Success
    </a><br>
    Interview with Michael J. Mauboussin<br>
    by Samuel Arbesman<br>
    Wired, November 16, 2012
</address>
</div>
</div>

---

### Luck and Skill in Wealth | Hope in 330 Signals

<div class="row">
  <div class = "col-md-8">
    <img src = "./assets/fig/rps.png" height = 500px></img>
  </div>
  <div class="col-md-4">
    <br><br>
    <blockquote style="font-size:80%;line-height:20px;">
    "the large number of RPS that we have documented...implies that either U.S. stock markets are pervasively inefficient, or that the number of rationally priced sources of risk in equity returns for theorists to understand and explain is far larger than previously envisaged."
    </blockquote>
  </div>  
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href ="http://ssrn.com/abstract=2062464">
      The Supraview of Return Predictive Signals
    </a><br>
    Green, Jeremiah and Hand, John R. M. and Zhang, Frank<br>
    Review of Accounting Studies, Forthcoming
</address>
</div>
</div>

---

### Luck and Skill in Wealth | Hope in Blind Monkeys

<div class="row">
  <div class = "col-md-12">
    <img src = "./assets/fig/arnott_monkeys.png" height = 500px></img>
  </div>
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href ="http://bit.ly/1bcOAh3">
      The Surprising Alpha from Malkiel's Monkey and Upside-Down Strategies
    </a><br>
    Arnott, Robert D., et al.
    The Journal of Portfolio Management 39.4 (2013): 91-105.
</address>
</div>
</div>

---

### Luck and Skill in Wealth | Hope in Passive

<div class="row">
  <div class = "col-md-12">
    <img src = "./assets/fig/morningstar_passive_us.png" height = 300px></img>
  </div>
</div>
<div class="row">
  <div class="col-md-8 col-md-offset-4">
    <img src = "./assets/fig/morningstar_passive_other.png" height = 200px
  </div>  
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href ="http://ibd.morningstar.com/article/article.asp?id=624328&CN=brf295,http://ibd.morningstar.com/archive/archive.asp?inputs=days=14;frmtId=12,%20brf295">
      A Bull Market in Passive Investing
    </a><br>
    Adam Zoll<br>
    Morningstar<br>
    January 6, 2014
</address>
</div>
</div>

---

### Skill | How to Get It?

<div class="row">
  <div class = "col-md-8">
    <br>
    <img src = "./assets/fig/deliberate_practice.png" height = 350px></img>
  </div>
  <div class="col-md-4">
    <br><br>
    <blockquote style="font-size:80%;line-height:20px;">
    "But the data indicate that there is an enormous amount of variability in deliberate practice-even in elite performers.  One player in Gobet and Campitelli's (2007) chess sample took 26 years of serious involvement in chess to reach a master level, while another player took less than 2 years to reach this level."
    </blockquote>
  </div>  
</div>

<div class = "row">
<div class = "col-md-4 col-md-offset-8">
<address class="text-muted">
    <a href =http://www.castonline.ilstu.edu/smith/405/readings_pdf/hambrick_deliberate_practice_2013.pdf">
      Deliberate practice: Is that all it takes to become an expert?
    </a><br>
    Hambrick, David Z., et al.<br>
    Intelligence<br>
    
</address>
</div>
</div>

---

### Accumulated Advice

> - Open Source Yourself
> - Engage and Find a Mentor or Pair Learn with Peer
> - Practice Telling Stories / Produce Content
> - Learn to Program/Code
> - Fail and Get Used to Being Wrong






