---
title: Anything and Everything
author: TimelyPortfolio
license: by-nc-sa
widgets: [mathjax, bootstrap]
github: {user: timelyportfolio, repo: talks/2014-04-15_UofA}
mode: selfcontained
hitheme: solarized_light
assets:
  css:
  - "http://fonts.googleapis.com/css?family=Raleway:300"
  - "http://fonts.googleapis.com/css?family=Oxygen"
--- dt:10
  
<style>
iframe.rChart{
  height:450px;
  width:100%;
  margin:auto auto;
}

body{
  font-family: 'Oxygen', sans-serif;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

h3 {
  background-color: #D4DAEC;
    text-indent: 100px; 
}

h4 {
  text-indent: 100px;
}

address {
  font-size: 9px;
  line-height: 14px;
  position: absolute;
  right:100px;
  width:300px;
}

</style>

```{r message = F, warning = F, error = F, echo = F, tidy = F, cache = F}
require(knitr)
opts_chunk$set(
  message = F,
  warning = F,
  echo = F,
  error = F,
  tidy = F,
  cache = F,
  fig.width = 11,
  fig.height = 5,
  results = 'asis'
)
```

# Why Am I Here?

---

# Why Are You Here?

--- 

### Forbes 400 (2013) | How They Made Their Money?

```{r}
require(rCharts)

wealthData <- data.frame(
  industry = c(
    "Investments","Technology","Real Estate","Fashion and Retail","Media","Food and Beverage","Energy","Healthcare","Sports","Manufacturing"
    ,"Investments","Service","Fashion and Retail","Energy","Food and Beverage","Media","Manufacturing","Real Estate","Diversified","Technology","Healthcare"
  )
  ,selfmade = c(rep(T,10),rep(F,11))
  ,freq = c(
    c(77,45,22,18,17,15,12,11,10,10)/273
    ,c(19,17,17,16,14,11,10,5,3,3,3)/(400-273)
  )
)

n1 <- nPlot(
  freq ~ industry
  ,group = "selfmade"
  ,data = wealthData
  ,type = "multiBarHorizontalChart"
)
n1$yAxis(
  tickFormat = "#! function(d) { return d3.format('0.2%')(d) }!#"
)
#n1

d1 <- dPlot(
  y = c("industry","selfmade")
  ,x = "freq"
  ,groups = "industry"
  ,data = wealthData
  ,type = "line"
  ,defaultColors = "#!d3.scale.category20()!#"
  ,height = 700
  ,width = 900
  ,bounds = list( x = 250, y = 50, width = 650, height = 470)
)
d1$xAxis(
  type = "addMeasureAxis"
  ,outputFormat = "0.2%"
)
d1$yAxis(
  type = "addCategoryAxis"
  ,orderRule = "freq"
)
d1
```
<address class="text-muted" style="font-size:8px;">
    <a href = "http://www.forbes.com/sites/erincarlyle/2013/09/18/how-self-made-forbes-400-billionaires-earned-their-money/">
    How Self-Made Forbes 400 Billionaires Earned Their Money
    </a><br>
    Erin Carlyle<br>
    Forbes September 18, 2013<br>
</address>


--- dt:10

### Forbes 400 (2013) | How They Made Their Money? | Bar Chart


```{r}
d2 <- dPlot(
  y = c("industry","selfmade")
  ,x = "freq"
  ,groups = "selfmade"
  ,data = wealthData
  ,type = "bar"
  ,defaultColors = "#!d3.scale.category20()!#"
  ,height = 700
  ,width = 900
  ,bounds = list( x = 250, y = 50, width = 650, height = 470)
)
d2$xAxis(
  type = "addMeasureAxis"
  ,outputFormat = "0.2%"
)
d2$yAxis(
  type = "addCategoryAxis"
  ,orderRule = "freq"
)
d2
```

<address class="text-muted">
    <a href = "http://www.forbes.com/sites/erincarlyle/2013/09/18/how-self-made-forbes-400-billionaires-earned-their-money/">
    How Self-Made Forbes 400 Billionaires Earned Their Money
    </a><br>
    Erin Carlyle<br>
    Forbes September 18, 2013<br>
</address>

---

### What You Might Not Know About Becoming Ultra-Wealthy?

[]()
